% \documentclass[11pt, twocolumn]{article}
\documentclass[11pt]{article}   
\usepackage{titlesec}
\usepackage{algorithm2e}
\usepackage[usenames]{color}
\usepackage{lineno}

\setcounter{secnumdepth}{4}

\titleformat{\paragraph}
{\normalfont\normalsize\bfseries}{\theparagraph}{1em}{}
\titlespacing*{\paragraph}
{0pt}{3.25ex plus 1ex minus .2ex}{1.5ex plus .2ex}

\usepackage{inputenc}
\usepackage{tikz}
\usetikzlibrary{shapes,arrows}
\usepackage{geometry}                		% See geometry.pdf to learn the
\usepackage{fixltx2e}
\geometry{letterpaper}                   		% ... or a4paper or
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{sectsty}
\usepackage{wrapfig}
\usepackage{color}
\usepackage{subfigure}
\usepackage[font={bf,small},labelsep=colon]{caption}
\usepackage{authblk}
\usepackage{booktabs}               % For drawing a table
\usepackage{listings}               % For drawing a table

%\usepackage[sort&compress, numbers]{natbib}

% \usepackage{times} % Use Times Font (appear like fonts in MS Word)
%\usepackage{mathptmx}

%\usepackage[parfill]{parskip}    		
% Activate to begin paragraphs with an empty line rather than an indent 

\usepackage{graphicx}				% Use pdf, png, jpg, or eps§
\usepackage{caption}
%\usepackage{subcaption}            % Use of subcaption, do not understand
\usepackage{hyperref}


% \usepackage[none]{hyphenat} % prevent hypenating; not a good idea

\newcommand*{\TitleFont}{%
       \usefont{\encodingdefault}{\rmdefault}{b}{n}%
       \fontsize{14}{14}%
       \selectfont}
\newcommand\abs[1]{\left|#1\right|} % Defination of absolute value

\geometry{
  body={6.5in, 9.0in},
  left=1.0in,
  top=1.0in
}

\tikzstyle{decision} = [diamond, draw, fill=blue!20, 
    text width=4.5em, text badly centered, node distance=3cm, inner sep=0pt]
\tikzstyle{block} = [rectangle, draw, fill=blue!20, 
    text width=6em, text centered, rounded corners, minimum height=4em]
\tikzstyle{line} = [draw, -latex']
\tikzstyle{cloud} = [draw, ellipse,fill=red!20, node distance=3cm,
    minimum height=2em]

%\renewcommand{\baselinestretch}{1.25}
\renewcommand{\baselinestretch}{1}
%\sectionfont{\normalsize}
%\subsectionfont{\normalsize}

\title{User guide for CFD--DEM solver lammpsFoam}

\author[1]{Rui Sun\thanks{Email: sunrui@vt.edu}}
\author[2]{Prachant Gupta}
\author[1]{Heng Xiao\thanks{Email: hengxiao@vt.edu}}
\author[2]{Jin Sun}

\affil[1]{Department of Aerospace and Ocean Engineering, Virginia Tech, United States}

\affil[2]{Institute for Infrastructure and Environment, The University of Edinburgh, UK}

\renewcommand\Authands{ and }

\date{}
\begin{document}

\maketitle

\section{Introduction}

Here is the brief introduction of demFoam, a toolbox of CFD--DEM simulation:

``demFoam'' is the name of this toolbox. 

``lammpsFoam'' is an open source CFD--DEM solver combining the LAMMPS and openFoam.

``LAMMPS'' is an open source molecular dynamics code that perform DEM simulations.

``OpenFOAM'' is an open source toolbox for CFD simulations.

The structure of the demFoam is like this:

\begin{lstlisting}
    demFoam
    |----Allwclean.sh
    |----Allwmake.sh
    |----cases/
    |----documentation/
    |----interfaceToLammps/
    |----lammpsFoam/
    |----readme/
\end{lstlisting}

``Allwclean.sh'' and ``Allwmake.sh'' are written to help with the compilation of lammpsFoam, the
CFD--DEM solver in demFoam. ``Allwmake.sh'' will help you install lammpsFoam while ``Allclean.sh''
will uninstall lammpsFoam. Note that the source file of LAMMPS is not included in demFoam. We highly
recommend you use lammps-1Feb14, a version released on February 2014.

All numerical cases are placed in ``demFoam/cases/'', including verification cases and validations cases.

Some documents are in ``demFoam/documentation/'', with a basic user manual (userManual.tex).

``demFoam/interfaceToLammps/'' and ``demFoam/lammpsFoam/'' are folders containing the source code of
lammpsFoam. To compile lammpsFoam, the files of ``demFoam/interfaceToLammps/'' should be copied to
``LAMMPS-(some version)/src''.
Allwclean.sh are Allwmake.sh written to help with the compilation of lammpsFoam, the CFD--DEM solver

\section{How to install lammpsFoam on your linux machine?}

Although Allwmake.sh can automatically help you with the installation of lammpsFoam, it is necessary
to demonstrate individual steps in the compilation.

\subsection{Environment for lammpsFoam}
The CFD-DEM solver lammpsFoam would be successfully installed on a machine with OpenFOAM and LAMMPS.
Here are the steps to compile it on your linux machine:
\begin{enumerate}
    \item Install OpenFOAM on your machine, the up-to-date lammpsFoam is supported for OpenFOAM
        2.1.1.
    \item Copy all the files in ``InterfaceToLammps'' folder to ``lammps-1Feb14/src", or create a
        soft link of the files.
    \item Change to ``lammps-1Feb14/src/STUBS''. Use command ``make''.
    \item Change to the ``lammps-1Feb14/src'' folder. Use command ``make yes-granular'' to install
        the granular package of LAMMPS. Add ``kspace'', ``manybody'', ``molecule'', ``fld'' as well
        in a similar way.
    \item Go back to the ``lammps-1Feb14/src'' folder. Use command ``make shanghailinux'' to
        generate an executable file named ``lmp\_shanghailinux'' in this folder. It may take a
        while.
    \item Stay at ``lammps-1Feb14/src'' folder. Use command ``make shlib'' to generate a new
        ``Makefile.shlib'' file.
    \item Stay at ``lammps-1Feb14/src'' folder. Use command ``make -f Makefile.shlib shanghailinux''
        to compile LAMMPS to a dynamic library. After this step, you will see a file named
        ``liblammps\_shanghailinux.so".
    \item Change to ``\$FOAM\_USER\_LIBBIN'' and make a soft link of ``liblammps\_shanghailinux.so"
        in this folder. ``liblammps\_shanghailinux.so'' is the file generated in the previous step.
    \item Change to ``LammpsFoam'' folder. Use command ``wmake libso dragModels'' to compile the
        drag models. Use command ``wmake libso chPressureGrad'' to compile the pressure gradient for
        channel flow.
    \item Stay at the same directory. Use command ``wmake'' to compile lammpsFoam.
\end{enumerate}

To check if your lammpsFoam is succesfully compiled, you can:
\begin{enumerate}
    \item Change to the ``cases/auto-testing/test-cases/xiaocase3/'' folder. 
    \item Execute ``./Allrun.sh'' in the command line to see the result.
\end{enumerate}

\section{Cases and supporting publications}

There are lot of publications using
lammpsFoam~\cite{sun09,xiao-cicp,gupta11a,gupta11b,gupta11b,gxs11a,gupta13a,gupta12,part1,part2}:

Several cases from the publications are added in ``demfoam/cases/auto-testing/test-cases'':
\begin{enumerate}
    \item ``xiaocase1'' is the 1st case in H. Xiao et al.'s paper~\cite{xiao-cicp}.
    \item ``xiaocase3'' is the 3rd case in H. Xiao et al.'s paper~\cite{xiao-cicp}.
    \item ``expMuller09'' is the case in R. Sun et al.'s paper~\cite{part1,part2}.
\end{enumerate}

\bibliographystyle{unsrt}
\bibliography{userGuide}

\end{document}

